The transboundary nature of the world’s exploited marine species

### 2021-04-06 Scripts/Manuscript_Draft.Rmd
Misc. for thesis submission

---
output:
  bookdown::word_document2:
  # bookdown::pdf_book:
    toc: no
    keep_tex: no
    number_sections: yes
    fig_width: 6
    fig_height: 4
# geometry: margin=1in
bibliography: ../References/FishForVisa_Ref.bib
# csl: ../References/nature_cc.csl
---

@@

<!-- ## References -->

<!-- <div id="refs"></div> -->

<!-- ## Supplements -->

```{r supplements, child = 'supplements.Rmd', eval = T}
```

>>>>

---
output:
  bookdown::pdf_book:
    toc: no
    keep_tex: no
    number_sections: yes
    fig_width: 6
    fig_height: 4
    latex_engine: xelatex
header-includes:
   - \usepackage[utf8]{inputenc}
# geometry: margin=1in
bibliography: ../References/FishForVisa_Ref.bib
# csl: ../References/nature_cc.csl
---

@@
